%%
%% The following code sets up the document formatting
%%

%this assumes that res_yy.sty is in some path
\documentstyle[hyperref, margin, line]{res_yy}


\hypersetup{backref,pdfpagemode=Full,colorlinks=true,backref}

\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\voffset}{-0.30in}
\addtolength{\textwidth}{1.00in} \addtolength{\textheight}{1.50in}

\renewcommand{\namefont}{\LARGE\emph}



%%
%% The following code defines some macros for terms which have raised font
%% (ie 4\fourth would result 4th with the 'th' raised (superscripted)
%%

\def\Cplusplus{{C\raise.5ex\hbox{\small ++}}}
\def\CSharp{{C\raise.5ex\hbox{\small \#}}}
% 'st' 'nd' 'rd' 'th' superscripts for numbers
\def\first{{\raise.5ex\hbox{\small st}}}
\def\second{{\raise.5ex\hbox{\small nd}}}
\def\third{{\raise.5ex\hbox{\small rd}}}
\def\fourth{{\raise.5ex\hbox{\small th}}}

%%
%% starting the actual document
%%

%\usepackage{fontspec}
%\usepackage{color}
%\usepackage[usenames,dvipsnames]{color}

\begin{document}
%\setmainfont{Adobe Garamond Pro}

\setlength{\parindent}{0pt}
\setlength{\hangindent}{0pt}
\setlength{\leftskip}{0pt}
% \setlength{\parskip}{8pt}

%\newcommand{\tt}[1]{\texttt{#1}}

\definecolor{dark-blue}{rgb}{0,0,0.12}
% \definecolor{dark-blue}{rgb}{0,0,1}
\newcommand{\blue}[1]{\textcolor{dark-blue}{#1}}
\definecolor{brass}{rgb}{0.12,0.12,0}
% \definecolor{brass}{rgb}{0.5,0.5,0}
\newcommand{\brass}[1]{\textcolor{brass}{#1}}
\newcommand{\headstyle}[1]{\blue{#1}}

\newcommand{\FIXME}[1]{\textcolor{red}{\emph{FIXME #1}}}
\newcommand{\kw}[1]{\blue{#1}}
\newcommand{\heavy}[1]{\textbf{#1}}

\name{\brass{Zachary McCord}}

\address{
\brass{
{\tt zjmccord@gmail.com} \hskip 3cm 185 Hudson St, Somerville, MA 02144 \hskip 3cm 847.754.7987}
}

\begin{resume}
\end{resume}


\section{\brass{\textsc{Education}}}

\headstyle{
\textbf{Carnegie Mellon University} \hfill August 2006 - December 2010\\
}
B.S. in Computer Science with a minor in Mathematical Sciences.
%% GPA of $3.\bar0$.

%%
%% the meat of the resume starts now
%%

\begin{formatb}
\employer{l}\title{r}\\
\location{l}\dates{r}\\
\body\\
\end{formatb}

%\section{\brass{\textsc{Objective}}}
%
%I'm motivated most by learning and novelty and work best in a small to medium group. Since
%I'm still finding my interests and talents I'm looking particularly for a position where the work
%is both varied and challenging. 

\section{\brass{\textsc{Skills}}}
\begin{description}
\item[\headstyle{Systems}]
Experience developing on \kw{Linux}, \kw{Mac OS X}, \kw{Windows} and \kw{Atmel
AVR-8}.
\item[\headstyle{Languages}]
Proficient in \kw{Python}, \kw{Django}, \kw{C} and \kw{\Cplusplus};
also have experience with \kw{bash}, \kw{HTML 5}/\kw{Javascript},
\kw{Qt}, \kw{Java}, \kw{Verilog}, various functional languages and \kw{OpenGL}.
% \kw{\CSharp}, \kw{Objective-C}, 
% \kw{Perl}, \kw{Ruby}, \kw{\LaTeX}, the \kw{ML} family, \kw{Haskell}, \kw{Lisp}/\kw{Scheme}
%% \item[\headstyle{Tools}]
%% Most comfortable with \kw{git}/\kw{vim}/\kw{bash};
%% also have experience with \kw{XCode}, \kw{Eclipse}, \kw{Visual Studio}, \kw{doxygen}, \kw{mercurial} and \kw{svn}.
\item[\headstyle{Work Style}]
I comment my code and work best as part of a small team.

\end{description}

\section{\brass{\textsc{History}}}

\headstyle{
\textbf{Elysium Digital, LLC}                 \hfill Computer Scientist \\
Boston, MA                                    \hfill June 2012 - Present \\
}
Provided consulting expertise to client law firms as well as performing
internal software DevOps. My DevOps role was on our internal
\kw{Python}/\kw{Django}-based portal, which Elysium employees, managers and
accountants use to track
time, plan budgets, analyse work patterns and track court orders.

\begin{itemize}
\item Led the team to complete major new features
\item Redesigned unsatisfactory parts of our database schema
\item Staged, QA-tested and deployed new releases, and provided ongoing support
\item Worked with users to clarify their needs and design features to satisfy
those needs within the available development budget
\item Started the (ongoing) process of replacing parts of the portal
with off-the-shelf software
\end{itemize}

Additionally, in my litigation consultant role I supported clients' litigation
by examining source code, writing lay summary documents on various
technologies, and appearing in court. Technologies involved included
\kw{information retrieval}, \kw{Java}, \kw{Dalvik}, \kw{compilers} and
\kw{gesture-based UIs}.
%% \setlength{\parskip}{8pt}

\headstyle{
\textbf{Pittsburgh Pattern Recognition, Inc. (now part of Google)} \hfill Intern \\
Pittsburgh, PA                                            \hfill April to July 2011\\
}
Wrote the first live, interactive face recognition and tracking demo for
PittPatt's SDK, and caught several product bugs before they affected customers.
%% \setlength{\parskip}{8pt}

\headstyle{
\textbf{School of Computer Science, Carnegie Mellon University} \hfill Teaching Assistant \\
Pittsburgh, PA                                                  \hfill January to May 2011\\
}
%% \setlength{\parskip}{0pt}
Created assignments and built course infrastructure for 15-495, \kw{Information Forensics}.
%% \setlength{\parskip}{8pt}

\headstyle{
\textbf{Language Technologies Institute, Carnegie Mellon University} \hfill Student Researcher\\
Pittsburgh, PA \hfill October 2008 to August 2009\\
}
%% \setlength{\parskip}{0pt}
Student researcher under Professor Noah Smith.
I researched handwritten and meachine-learned grammars for a novel task and processed data on a \kw{Condor} grid.

%I performed open-ended research and supported other researchers within the ARK
%research group:
%% \begin{itemize}
%% \item Managed and processed data on
%%       our 20-node \kw{Condor} computing grid.
%% \item Researched handwritten and machine-learned grammars for a novel quote
%%       extraction task.
%% \end{itemize}
%% \setlength{\parskip}{8pt}

\headstyle{
\textbf{Robotics Institute, Carnegie Mellon University} \hfill  Student Researcher \\
Pittsburgh, PA                                          \hfill  September 2006
to August 2007\\
}
%% \setlength{\parskip}{0pt}
Worked with a ten-person team to write desktop robot control software and
robot firmware as well as build the robots themselves.

\section{\brass{\textsc{Coursework}}}
\headstyle{
\textbf{Operating Systems Design and Implementation} \hfill Carnegie Mellon
University, Fall 2010\\
}
My partner and I wrote the first \kw{\Cplusplus}\ kernel
ever submitted in the class, as the kernel is traditionally written in
straight \kw{C}.

%% \headstyle{
%% \textbf{Introduction to Computer Architecture}
%% }
%% 
%% Our team of 3 designed a simple, pipelined MIPS-like processor core in
%% \kw{Verilog}.
%% 
%% \headstyle{
%% \textbf{Introduction to Natural Language Processing}
%% }
%% 
%% Our team of 3 wrote a question answering system based on Wikipedia articles,
%% using \kw{SML} and \kw{Perl}.


%%
%% We use the same formatting for projects as for work experience
%% Shown below is the formatting used previously
%%
%%  \begin{formatb}
%%    \employer{l}\title{r}\\
%%    \location{l}\dates{r}\\
%%    \body\\
%%  \end{formatb}
%%
%% 
%%  Note that \location is now being used for non-location information
%%

\section{\brass{\textsc{Interests}}}
In my free time, I work on projects ranging across \kw{machine translation},
\kw{Android} apps, productivity tools, browser games, and \kw{3D printing}, among other pursuits.

\begin{formatb}
  \employer{l}\dates{r}\\
  \body\\
\end{formatb}

\section{\brass{\textsc{Publications}}}

\headstyle{
\textbf{Design of a Modular Snake Robot} \hfill IROS 2007\\
}
Cornell Wright, Aaron Johnson, Aaron Peck, Zachary McCord, Allison Naaktgeboren, Philip Gianfortoni, Manuel Gonzalez-Rivero, Ross Hatton, and Howie Choset

%%  \section{\brass{\textsc{References}}}
%%  
%%  \begin{description}
%%  \item[\headstyle{Michael A. Sipe, Ph.D.}] VP of Product Development, Pittsburgh
%%  Pattern Recognition, Inc.\\
%%  \texttt{sipe@ieee.org}. 
%%  \item[\headstyle{Brian R. Colonna}] Software Engineer, Pittsburgh Pattern
%%  Recognition, Inc.\\
%%  \texttt{brian.r.colonna@gmail.com}. 
%%  \item[\headstyle{Prof. Noah Smith}] Associate Professor, Language Technologies Institute, Carnegie
%%  Mellon University. \texttt{nasmith@cs.cmu.edu}
%%  %\item Andrew Drake. \texttt{adrake@andrew.cmu.edu}. My Operating Systems partner.
%%  \end{description}

\end{document}
